### 2014-10-24 ThesisJo/derivations.tex
la2pdf commit - 2014:10:20	18:25:51	(Mon20.Oct)
la2pdf commit - 2014:10:20	21:07:17	(Mon20.Oct)
la2pdf commit - 2014:10:20	21:37:26	(Mon20.Oct)
Added derivation of Rayleigh specular formula
la2pdf commit - 2014:10:24	17:34:47	(Fri24.Oct)

@@

To see how roughness affects the specular reflection we compute the mean reflected wave as
\begin{align}
<p> &= \int\limits_{-\infty}^{\infty} e^{-j\Delta\varphi(\xi)} p(\xi) d\xi,
\end{align}
where $p(\xi)$ is the probability density function of $\xi$. If we assume normal distribution, we get:
\begin{align}
<p> &= \int\limits_{-\infty}^{\infty} e^{-j2k\xi\cos\theta} \frac{1}{\sqrt{2\pi}\sigma_{\!\xi}}e^{-\frac{\xi^2}{2\sigma_{\!\xi}^2}} d\xi \nn
&= \frac{1}{\sqrt{2\pi}\sigma_{\!\xi}} \int\limits_{-\infty}^{\infty} e^{-j2k\xi\cos\theta} e^{-\frac{\xi^2}{2\sigma_{\!\xi}^2}} d\xi \nn
\end{align}

\begin{align}
p(\xi) = \frac{1}{\sqrt{2\pi}\sigma_{\!\xi}}e^{-\frac{\xi^2}{2\sigma_{\!\xi}^2}}
\end{align}

\begin{align}
p(\xi) = \frac{1}{\sqrt{2\pi}\sigma_{\!\xi}}e^{-\frac{\xi^2}{2\sigma_{\!\xi}^2}}
\end{align}

>>>>

\section{Wave Equation}

\begin{table}[!b]\centering%\normalsize
\begin{tabular}[c]{l r r r@{}  l}\hline
\rowcolor{tabBlue} & \multicolumn{1}{>{\columncolor{tabBlue}}c}{\bf B$_\text{arith}$} & \multicolumn{1}{>{\columncolor{tabBlue}}c}{\bf B$_\text{mem}$} & \multicolumn{2}{>{\columncolor{tabBlue}}c}{\bf B$_\text{mem}$/B$_\text{arith}$} \\\hline
Arithmetic & 1.03 Tflop/s & & &\\
Global memory & & 36 Gfloats/s & \hspace{30pt} 1 &:30 \\
Shared memory & & 257 Gfloats/s & 1 &:4 \\
Registers & & $>$1.5 Tfloats/s & $>$3 &:2~\cite{Vasilyy}
\end{tabular}
\caption{Nvidia Quadro 6000: Memory throughput, $B_{\lowercase{\text{mem}}}$, compared to arithmetic throughput, $B_\text{arith}$.}\label{throughputs}
\end{table}%

@@

To see how roughness affects the specular reflection we compute the mean reflected wave as
\begin{align}
<p> &= V\int\limits_{-\infty}^{\infty} e^{-j\Delta\varphi(\xi)} p(\xi) d\xi,
\end{align}
where $p(\xi)$ is the probability density function of $\xi$. If we assume normal distribution, we get:
\begin{align}
<p> &= V\int\limits_{-\infty}^{\infty} e^{-j2k\xi\cos\theta} \frac{1}{\sqrt{2\pi}\sigma}e^{-\frac{\xi^2}{2\sigma^2}} d\xi \nn
&= \frac{V}{\sqrt{2\pi}\sigma} \int\limits_{-\infty}^{\infty} e^{-\frac{\xi^2}{2\sigma^2}-j2k\xi\cos\theta} d\xi &\Big|{\begin{matrix}\scriptscriptstyle\hspace{-0.64cm} a = \frac{1}{2\sigma^2}\\
\scriptscriptstyle b = -j2k\cos\theta\end{matrix}}\nn
&= A \int\limits_{-\infty}^{\infty} e^{-a\xi^2 + b\xi} d\xi \nn
&= A \int\limits_{-\infty}^{\infty} e^{-a(\xi - \frac{b}{2a})^2 - \frac{b^2}{4a}} d\xi \nn
&= A e^{\frac{-b^2}{4a}} \int\limits_{-\infty}^{\infty} e^{-a(\xi - \frac{b}{2a})^2} d\xi & \Big|_{y = \xi - \frac{b}{2a}}\nn
&= A e^{\frac{-b^2}{4a}} \int\limits_{-\infty}^{\infty} e^{-ay^2} dy & \Big|_{z = \sqrt{a} y}\nn
&= A e^{\frac{-b^2}{4a}}\frac{1}{\sqrt{a}} \int\limits_{-\infty}^{\infty} e^{-z^2} dz \nn
&= A e^{\frac{-b^2}{4a}}\sqrt{\frac{\pi}{a}} \nn
&= \frac{V}{\sqrt{2\pi}\sigma} \sqrt{\frac{\pi}{\frac{1}{2\sigma^2}}} e^{\frac{-(-j2k\cos\theta)^2}{4\frac{1}{2\sigma^2}}} \nn
&= V e^{-2k^2\sigma^2\cos^2\theta}
\end{align}
This reflection coefficient is valid when the Rayleigh parameter is small (i.e. small frequency and relief amplitude), and at grazing incidence. Conventional limit of validity is $\frac{\pi}{2}$, which corresponds to $\sigma = \frac{\lambda}{8\cos\theta}$ and a coherent loss of 10.7dB.
